Exploratory data analysis

### 2021-07-12 slides/data_checking.Rmd
graph expertise conf ~ recall

```{r}
q_demos %>% 
  ggplot(aes(x = trivia_skill_self, y = j_score)) +
  geom_abline(slope = .01, intercept = 0, linetype = "dotted") +
  geom_point(size = 3) +
  expand_limits(y = 0) +
  labs(x = "Self-reported trivia expertise (relative to 'average person')",
       y = "Expertise score on Jeopardy audition test") +
  theme_bw()
```

@@

@@

```{r}
q_demos %>%
  select(subj_num, starts_with("trivia"), j_score) %>% 
  mutate(j_score = j_score * 100) %>% 
  pivot_longer(cols = -subj_num, names_to = "var", values_to = "value") %>% 
  ggplot(aes(x = value)) + geom_histogram() + facet_wrap(~ var)
```

>>>>

```{r}
q_trivia_demos %>% 
  ggplot(aes(x = trivia_skill_self, y = j_score)) +
  geom_abline(slope = .01, intercept = 0, linetype = "dotted") +
  geom_point(size = 3) +
  expand_limits(y = 0) +
  labs(x = "Self-reported trivia expertise (relative to 'average person')",
       y = "Expertise score on Jeopardy audition test") +
  theme_bw()
```

@@

```{r}
j_recall %>% 
  ggplot(aes(x = acc_recall, y = resp_conf, color = j_score, fill = j_score)) + 
  geom_jitter(alpha = 0.3, width = 0.05) + 
  geom_smooth(aes(group = subj_num), method = "lm", formula = y ~ x, se = FALSE) + 
  scale_color_viridis_c() +
  scale_fill_viridis_c() +
  labs(x = "Recall accuracy (strict)", y = "Recall confidence", color = "Expertise score", fill = "Expertise score") +
  theme_bw()
```

@@

```{r}
q_trivia_demos %>%
  select(subj_num, starts_with("trivia"), j_score) %>% 
  mutate(j_score = j_score * 100) %>% 
  pivot_longer(cols = -subj_num, names_to = "var", values_to = "value") %>% 
  ggplot(aes(x = value)) + geom_histogram() + facet_wrap(~ var)
```
